---
title: "Title of your report"
author: 'Liana Poghosyan'
output: pdf_document
---

DEADLINE: July 20


Setup chunk
call all libraries in this chunk
set echo=F, message=f, warning=F. Your report should not have any visible R code in the pdf.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
library(ggplot2)
```


## The problem/data description
- Why is this important/interesting
- The problem statement
-Where does the data come from?
-What was done on this data so far

## Main hypotheses
Here you write what are you trying to find in the data, what are some hypotheses that you are trying to test

## Analysis

## Summary of findings and recommendatins if any



Some text here
Plot - all the plots need to have meaningful guides (titles, etc)

plot should have size: fig.width = 4, fig.height = 4. You can change this parameter only if it is very much needed for good visualization.

```{r, fig.width=4, fig.height=4}
# 
data(mtcars)
ggplot(mtcars, aes(hp,mpg)) + geom_point() + 
  labs(x = "Horsepower", y = 'Miles per gallon', title = 'relationship between mpg and hp')
```

Again some text. Dont make consecutive plots in a row without any text inside.


Overall 6-8 pages.


